\documentclass[11pt,largemargins]{homework}

\newcommand{\hwname}{YOUR NAME HERE}
\newcommand{\hwemail}{YOUR ANDREW ID HERE}
\newcommand{\hwtype}{Homework}
\newcommand{\hwnum}{1}
\newcommand{\hwclass}{07-131}
\newcommand{\hwlecture}{1}
\newcommand{\hwsection}{A}

\begin{document}
\maketitle

\question
You failed to use up all your blocks this semester, so you after learning some useful knowledge, you devised a brilliant to use your blocks for the spring semester. 

You will start slow and use 2 blocks on the first week, then 4 blocks in the next week, 6 in the week after that, then 8, and so on until the end of the semester. Your non-GPI friend disagrees and doesn't think that this will put you on track to use up all 205 blocks*. To win the argument, prove that $2(1+2+3+...n) \leq n(n+1)$. With n \(=\) number of weeks. There are 15 weeks in the semester, thus, at the end of the next semester, you will have used up (\(15*16 =\)) 240 blocks, helping you spend some of your dinex too! 

Put formally, 
\begin{center}
    For any \(n \in \mathbb{N}\) define \(S_n = 2(\sum_{i = 1}^{n}{i})\). Prove \[\forall n \in N, \, S_n = n(n+1)\]
\end{center}

\begin{proof}
% Your proof goes here!
\end{proof}	

*Note: RIP if you have the green/blue plan

\newpage

\question
As you may know, there is a magical table by the sixth floor commons in Gates where free food appears with some regularity. As a college student, you are keenly interested in free food and wonder how long you could subsist solely on free food from the magic table.

Assume that free food appears every day with probability \(p\), and that you must eat every day. For any given number of days \(k\), derive the probability that you can subsist for at least \(k\) days on free food. Use induction.

\begin{proof}
% Your proof goes here!
\end{proof}

\end{document}
